\begin{frame}
    \frametitle{Outline} 
    \begin{flushleft}
        \tableofcontents[currentsection]
    \end{flushleft}
\end{frame} 

\begin{frame}
    \frametitle{Boxmodel Set-up}

    \begin{itemize}
        \item MECCA boxmodel using MCM v3.2 chemistry. \vspace{3mm}
        \item Seven day run time at equinoctical conditions. \vspace{3mm}
        \item Idealised NO conditions giving maximum \ce{O3} production. \vspace{3mm}
        \item Initial VOC mixing ratios held constant until noon of first day.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Emitted VOCs}
    \vspace{-2mm}

    \begin{itemize}
        \item Emitted VOCs typical for Los Angeles [Baker et al., AE, 2008].
    \end{itemize}
    \vspace{3mm}

    \begin{description}
        \item[Alkanes] Ethane, propane, butane, 2-methyl propane, pentane, 2-methyl butane, hexane, heptane, octane. 
        \item[Alkenes] Ethene, propene, butene, 2-methyl propene, isoprene. 
        \item[Aromatics] Benzene, toluene, m-xylene, o-xylene, p-xylene, ethylbenzene. 
    \end{description}
\end{frame}

\begin{frame}
    \frametitle{Tagging the MCM v3.2}
    \vspace{-5mm}

    \begin{columns}[onlytextwidth]
        \begin{column}{0.4\textwidth}
            \begin{flushleft}
                \input{tex_files/tagging_diagram}
            \end{flushleft}
        \end{column}%
        \begin{column}{0.55\textwidth}
            \begin{center}
                \begin{itemize}
                    \item Every organic degradation product labelled with emitted VOC name.
                    \item Each VOC has its own set of degradation reactions.
                    \item Tag used to allocate OH reactivity of degradation products to emitted VOC.
                \end{itemize}
            \end{center}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{OH Reactivity VOC Allocation}

    \begin{itemize}
        \item Calculate OH reactivity of each degradation product \\ (rate constant $\times$ non-OH reactant concentration). \vspace{2mm}
        \item Tag indicates VOC source of degradation product. \vspace{2mm}
        \item Sum all OH reactivities of each emitted VOC and \\ its degradation products. \vspace{2mm}
        \item Allocated OH reactivities integrated over each day and \\ night period.
    \end{itemize}
\end{frame}
